The Elements of Theses

### 2014-09-09 thesis/Conclusion.tex
offline -> batched

\chapter{Conclusion and Future Works}
\label{chap:concl}
Deduplication in storage backup with an ever-increasing demand faces 
scalability and throughput challenges.  This dissertation investigates 
scalable techniques in building a VM snapshot storage system that provides low-cost
deduplication support for large VM clouds.  In particular, our work focuses on 
three specific  aspects  of VM snapshot deduplication: a synchronous solution for offline duplicate detection,
a multi-level selective approach for inline deduplication, and data management on the top of
cloud file system with an emphasis on fault tolerance and garbage collection.
Our system  has  been  implemented on Xen-based Linux VM clusters.

>>>>

\chapter{Conclusion and Future Works}
\label{chap:concl}
Deduplication in storage backup with an ever-increasing demand faces
scalability and throughput challenges.  This dissertation investigates
scalable techniques in building a VM snapshot storage system that provides low-cost
deduplication support for large VM clouds.  In particular, our work focuses on
three specific  aspects  of VM snapshot deduplication: a synchronous solution for batched duplicate detection,
a multi-level selective approach for inline deduplication, and data management on the top of
cloud file system with an emphasis on fault tolerance and garbage collection.
Our system  has  been  implemented on Xen-based Linux VM clusters.
